BOLD Parameter Estimation Using Particle Filters

### 2010-12-13 doc/thesis/resultsB.tex
updated thesis for first ETD

\begin{figure}[H]
\centering
\subfigure[Axial Slices]{\label{fig:hm_pfilter} \includegraphics[scale=.85]{images/pfilter_hm}}
\subfigure[Sagittal Slice]{\label{fig:hm_canon_pfilter_x} \includegraphics[scale=3]{images/pfilter_hm_x}}
\subfigure[Coronal Slice]{\label{fig:hm_canon_pfilter_y} \includegraphics[scale=3]{images/pfilter_hm_y}}
\subfigure[Axial Slice]{\label{fig:hm_canon_pfilter_z} \includegraphics[scale=3]{images/pfilter_hm_z}}
\subfigure{\label{fig:scale_pfilter} \includegraphics[scale=.5]{images/scale2}}
\caption[Particle Filter Normalized Residual Results]{Particle Filter results measured in normalized error.
        Units of match is normalized residual where the lowest (best) levels shown are
        $0.7$ and the highest error shown (threshold) is $1$.
        Sagittal, coronal and axial slices are shwon in \autoref{fig:hm_canon_pfilter_x}.}
\label{fig:hm_canon_pfilter}
\end{figure}

@@

\begin{figure}[H]
\centering
\subfigure[Axial Slices]{\label{fig:hm_mi} \includegraphics[scale=.85]{images/mi_hm}}
\subfigure[Sagittal Slice]{\label{fig:hm_canon_mi_x} \includegraphics[scale=3]{images/mi_hm_x}}
\subfigure[Coronal Slice]{\label{fig:hm_canon_mi_y} \includegraphics[scale=3]{images/mi_hm_y}}
\subfigure[Axial Slice]{\label{fig:hm_canon_mi_z} \includegraphics[scale=3]{images/mi_hm_z}}
\subfigure{\label{fig:scale_mi} \includegraphics[scale=.5]{images/scale4}}
\caption[Particle Filter \acs{MI} Results]
        {Particle Filter results measured in \ac{MI}.
         Units of match is bits (standard for base-2 \ac{MI}). The highest (best) levels are
         $0.42$ and the worst shown (threshold) is $0.1$.}
\label{fig:hm_canon_pfilter_mi}
\end{figure}

%37-14-7
\begin{figure}
\centering
\subfigure[Particle Filter]{\label{fig:comp1pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/1_pfilter_37_14_7}}
\subfigure[SPM]{\label{fig:comp1spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/1_spm_37_14_7}}
\caption[Time Series Comparison, Section 1]{Section 1, Estimated vs. Actual \ac{BOLD} response. $t$-Score: $10.71$, \ac{MI}: $0.33$, Residual: $0.72$.}
\label{fig:comp1}
\end{figure}

%34-12-7
\begin{figure}
\centering
\subfigure[Particle Filter]{\label{fig:comp2pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/2_pfilter_34_12_7}}
\subfigure[SPM]{\label{fig:comp2spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/2_spm_34_12_7}}
\caption[Time Series Comparison, Section 2]{Section 2, Estimated vs. Actual \ac{BOLD} response. $t$-Score: $6.97$, \ac{MI}: $0.04$, Residual: $1.02$.}
\label{fig:comp2}
\end{figure}

%23-21-7
\begin{figure}
\centering
\subfigure[Particle Filter]{\label{fig:comp3pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/3_pfilter_23_21_7}}
\subfigure[SPM]{\label{fig:comp3spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/3_spm_23_21_7}}
\caption[Time Series Comparison, Section 3]{Section 3, Estimated vs. Actual \ac{BOLD} response. $t$-Score: $2.85$, \ac{MI}: $-0.03$, Residual: $0.81$.}
\label{fig:comp3}
\end{figure}

%33-30-4
\begin{figure}[H]
\centering
\subfigure[Particle Filter]{\label{fig:comp4pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/4_pfilter_26_15_7}}
\subfigure[SPM]{\label{fig:comp4spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/4_spm_26_15_7}}
\caption[Time Series Comparison, Section 4]{Section 4, Estimated vs. Actual \ac{BOLD} response. $t$-Score: $0.50$, \ac{MI}: $0.06$, Residual: $0.95$. }
\label{fig:comp4}
\end{figure}

% or in original coordinates 29-9-13
\begin{figure}
\centering
\subfigure[Particle Filter]{\label{fig:comp5pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/5_pfilter_29_9_13}}\\
\subfigure[SPM]{\label{fig:comp5spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/5_spm_29_9_13}}
\caption[Time Series Comparison, Section 5]{Section 5, Estimated vs. Actual \ac{BOLD} Response. $t$-Score: $4.17$, \ac{MI}: $0.02$, Residual: $1.14$.}
%\caption{Section 5, Below threshold in both particle filter checks, but above threshold in SPM. \ac{MI} of $0.0212822$, $t$-Value
%of $4.17399$ and $MSE$ of $1.14171$.}
\label{fig:comp5}
\end{figure}

%23-10-18 or in original coordinates 36-17-19
\begin{figure}
\centering
\subfigure[Particle Filter]{\label{fig:comp6pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/6_pfilter_36_17_19}}
\subfigure[SPM]{\label{fig:comp6spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/6_spm_36_17_19}}
\caption[Time Series Comparison, Section 6]{Section 6, Estimated vs. Actual \ac{BOLD} Response. $t$-Score: $2.49$, \ac{MI}: $.34$, Residual: $0.78$.}
%\caption{Section 6, MI of $0.335504$, T Value: $2.49154$, normalized error: $0.783348$ Not visible in SPM}
\label{fig:comp6}
\end{figure}

%16-19-0 or in original coordinates 29-26-1
\begin{figure}
\centering
\subfigure[Particle Filter]{\label{fig:comp7pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/7_pfilter_29_26_1}}
%\subfigure[SPM]{\label{fig:comp7spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/5_spm_25_34_25}}
\caption[Time Series Comparison, Section 7]{Section 7, Estimated vs. Actual \ac{BOLD} Response. $t$-Score: $1.32$, \ac{MI}: $0.11$, Residual: $1.10$.}
%\caption{Section 7, $.1052$ in MI, $1.31534$ in SPM (which left this flat) and $1.09992$ normalized $\sqrt{MSE}$. Only visible in MI map. }
\label{fig:comp7}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\subfigure[Axial Slices]{\label{fig:hm_pfilter} \includegraphics[scale=.85]{images/pfilter_hm}}
\subfigure[Sagittal Slice]{\label{fig:hm_canon_pfilter_x} \includegraphics[scale=3]{images/pfilter_hm_x}}
\subfigure[Coronal Slice]{\label{fig:hm_canon_pfilter_y} \includegraphics[scale=3]{images/pfilter_hm_y}}
\subfigure[Axial Slice]{\label{fig:hm_canon_pfilter_z} \includegraphics[scale=3]{images/pfilter_hm_z}}
\subfigure{\label{fig:scale_pfilter} \includegraphics[scale=.5]{images/scale2}}
\caption[Particle Filter results measured in normalized error.]
    {Particle Filter results measured in normalized error.
        Units of match is normalized residual where the lowest (best) levels shown are
        $0.7$ and the highest error shown (threshold) is $1$.
        Sagittal, coronal and axial slices are shwon in \autoref{fig:hm_canon_pfilter_x}.}
\label{fig:hm_canon_pfilter}
\end{figure}

@@

\begin{figure}[H]
\centering
\subfigure[Axial Slices]{\label{fig:hm_mi} \includegraphics[scale=.85]{images/mi_hm}}
\subfigure[Sagittal Slice]{\label{fig:hm_canon_mi_x} \includegraphics[scale=3]{images/mi_hm_x}}
\subfigure[Coronal Slice]{\label{fig:hm_canon_mi_y} \includegraphics[scale=3]{images/mi_hm_y}}
\subfigure[Axial Slice]{\label{fig:hm_canon_mi_z} \includegraphics[scale=3]{images/mi_hm_z}}
\subfigure{\label{fig:scale_mi} \includegraphics[scale=.5]{images/scale4}}
\caption[Particle Filter results measured in \ac{MI}.]
        {Particle Filter results measured in \ac{MI}.
         Units of match is bits (standard for base-2 \ac{MI}). The highest (best) levels are
         $0.42$ and the worst shown (threshold) is $0.1$.}
\label{fig:hm_canon_pfilter_mi}
\end{figure}

%37-14-7
\begin{figure}
\centering
\subfigure[Particle Filter]{\label{fig:comp1pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/1_pfilter_37_14_7}}
\subfigure[SPM]{\label{fig:comp1spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/1_spm_37_14_7}}
\caption[Time Series Comparison, Section 1]{Time Series Comparison, Section 1.
Estimated vs. Actual \ac{BOLD} response. $t$-Score: $10.71$, \ac{MI}: $0.33$, Residual: $0.72$.}
\label{fig:comp1}
\end{figure}

%34-12-7
\begin{figure}
\centering
\subfigure[Particle Filter]{\label{fig:comp2pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/2_pfilter_34_12_7}}
\subfigure[SPM]{\label{fig:comp2spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/2_spm_34_12_7}}
\caption[Time Series Comparison, Section 2]{Time Series Comparison, Section 2.
Estimated vs. Actual \ac{BOLD} response. $t$-Score: $6.97$, \ac{MI}: $0.04$, Residual: $1.02$.}
\label{fig:comp2}
\end{figure}

%23-21-7
\begin{figure}
\centering
\subfigure[Particle Filter]{\label{fig:comp3pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/3_pfilter_23_21_7}}
\subfigure[SPM]{\label{fig:comp3spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/3_spm_23_21_7}}
\caption[Time Series Comparison, Section 3]{Time Series Comparison, Section 3.
Estimated vs. Actual \ac{BOLD} response. $t$-Score: $2.85$, \ac{MI}: $-0.03$, Residual: $0.81$.}
\label{fig:comp3}
\end{figure}

%33-30-4
\begin{figure}[H]
\centering
\subfigure[Particle Filter]{\label{fig:comp4pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/4_pfilter_26_15_7}}
\subfigure[SPM]{\label{fig:comp4spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/4_spm_26_15_7}}
\caption[Time Series Comparison, Section 4]{Time Series Comparison, Section 4.
Estimated vs. Actual \ac{BOLD} response. $t$-Score: $0.50$, \ac{MI}: $0.06$, Residual: $0.95$. }
\label{fig:comp4}
\end{figure}

% or in original coordinates 29-9-13
\begin{figure}
\centering
\subfigure[Particle Filter]{\label{fig:comp5pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/5_pfilter_29_9_13}}\\
\subfigure[SPM]{\label{fig:comp5spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/5_spm_29_9_13}}
\caption[Time Series Comparison, Section 5]{Time Series Comparison, Section 5.
Estimated vs. Actual \ac{BOLD} Response. $t$-Score: $4.17$, \ac{MI}: $0.02$, Residual: $1.14$.}
%\caption{Section 5, Below threshold in both particle filter checks, but above threshold in SPM. \ac{MI} of $0.0212822$, $t$-Value
%of $4.17399$ and $MSE$ of $1.14171$.}
\label{fig:comp5}
\end{figure}

%23-10-18 or in original coordinates 36-17-19
\begin{figure}
\centering
\subfigure[Particle Filter]{\label{fig:comp6pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/6_pfilter_36_17_19}}
\subfigure[SPM]{\label{fig:comp6spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/6_spm_36_17_19}}
\caption[Time Series Comparison, Section 6]{Time Series Comparison, Section 6.
Estimated vs. Actual \ac{BOLD} Response. $t$-Score: $2.49$, \ac{MI}: $.34$, Residual: $0.78$.}
%\caption{Section 6, MI of $0.335504$, T Value: $2.49154$, normalized error: $0.783348$ Not visible in SPM}
\label{fig:comp6}
\end{figure}

%16-19-0 or in original coordinates 29-26-1
\begin{figure}
\centering
\subfigure[Particle Filter]{\label{fig:comp7pfilter} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/7_pfilter_29_26_1}}
%\subfigure[SPM]{\label{fig:comp7spm} \includegraphics[clip=true,trim=5cm 2.5cm 4cm 3cm,width=.93\textwidth]{images/5_spm_25_34_25}}
\caption[Time Series Comparison, Section 7]{Time Series Comparison, Section 7.
Estimated vs. Actual \ac{BOLD} Response. $t$-Score: $1.32$, \ac{MI}: $0.11$, Residual: $1.10$.}
%\caption{Section 7, $.1052$ in MI, $1.31534$ in SPM (which left this flat) and $1.09992$ normalized $\sqrt{MSE}$. Only visible in MI map. }
\label{fig:comp7}
\end{figure}

### 2010-12-13 doc/thesis/thesis.tex
lots of fixes from the corrections
just need to edit discussion/conclusion, change captions and copy some graphs from defense
just need to fix figure captions for multivoxel cases. And fix bib
finished I think
fixed all the acronyms, think I might be done
updated thesis for first ETD

\usepackage[printonlyused,withpage]{acronym}
\usepackage{colortbl}
\usepackage{times}
\usepackage[siunitx]{circuitikz}
%\usetikzlibrary{trees}
%\usetikzlibrary{shapes,snakes}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{cancel}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}
\def\chapterautorefname{Chapter}
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}

@@

August 30, 2010\\
Blacksburg, Virginia

@@

Keywords: BOLD Response, FMRI, Nonlinear Systems, Particle Filter, Bayesian Statistics, System Identification
\\
Copyright 2010, Micah C. Chambers

@@

\huge
\bfseries
List of Acronyms
\mdseries
\normalsize
\begin{acronym}[CMRO2]
\acro{BOLD}{Blood-Oxygen-Level-Dependent}
\acro{CBF}{Cerebral Blood Flow}
\acro{CBV}{Cerebral Blood Volume}
\acro{CMRO2}{Cerebral Metabolic Rate of Oxygen}
\acro{dHb}{Deoxygenated Hemoglobin}
\acro{EPI}{Echo Planar Imaging}
\acro{fMRI}{Functional Magnetic Resonance Imaging}
\acro{GLM}{General Linear Model}
\acro{HRF}{Hemodynamic Response Function}
\acro{Hb}{Hemoglobin}
\acro{MR}{Magnetic Resonance}
\acro{MRI}{Magnetic Resonance Imaging}
\acro{O2Hb}{Oxygenated Hemoglobin}
\acro{RF}{Radio Frequency}
\acro{SNR}{Signal-to-Noise Ratio}
\acro{SPM}{Statistical Parametric Mapping}
\acro{T1}{Longitudinal}
\acro{T2}{Spin-Spin}
\acro{TR}{Repetition Time}
\end{acronym}
\pagebreak

\pagenumbering{arabic}
\pagestyle{myheadings}

\include{intro}
\include{background}
\include{particlefilters}
\include{methods}
\include{results}
\include{resultsB}
\include{discussion}
\include{conclusion}

\bibliographystyle{plain}
%\bibliographystyle{abbrvnat}
%\bibliographystyle{apalike}
%\bibliographystyle{abbrvnat}
%\bibliographystyle{abbrv}
\bibliography{library}

>>>>

\usepackage[printonlyused,withpage]{acronym}
\usepackage{colortbl}
\usepackage{times}
\usepackage[siunitx]{circuitikz}
%\usetikzlibrary{trees}
%\usetikzlibrary{shapes,snakes}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{cancel}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}
\def\chapterautorefname{Chapter}
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}
\usepackage{chapterbib}

@@

September 14, 2010\\
Blacksburg, Virginia

@@

Keywords: BOLD Response, fMRI, Nonlinear Systems, Particle Filter, Bayesian Statistics, System Identification
\\
Copyright 2010, Micah C. Chambers

@@

\huge
\bfseries
List of Acronyms
\mdseries
\normalsize
\begin{acronym}[CMRO2]
\acro{BOLD}{Blood-Oxygen-Level-Dependent}
\acro{CBF}{Cerebral Blood Flow}
\acro{CBV}{Cerebral Blood Volume}
\acro{CMRO2}{Cerebral Metabolic Rate of Oxygen}
\acro{DC}{Direct Current}
\acro{dHb}{Deoxygenated Hemoglobin}
\acro{EM}{Expectation-Maximization}
\acro{EPI}{Echo Planar Imaging}
\acro{fMRI}{Functional Magnetic Resonance Imaging}
\acro{FMRIB}{Oxford Centre for Functional MRI of the Brain}
\acro{FSL}{FMRIB Software Library}
\acro{FWHM}{Full-Width Half-Maximum}
\acro{GA}{Genetic Algorithms}
\acro{GLM}{General Linear Model}
\acro{HRF}{Hemodynamic Response Function}
\acro{Hb}{Hemoglobin}
\acro{MAD}{Median Absolute Deviation}
\acro{MI}{Mutual Information}
\acro{MR}{Magnetic Resonance}
\acro{MRI}{Magnetic Resonance Imaging}
\acro{MSE}{Mean Squared Error}
\acro{O2Hb}{Oxygenated Hemoglobin}
\acro{ODE}{Ordinary Differential Equation}
\acro{PDF}{Probability Density Function}
\acro{POSSUM}{Physics-Oriented Simulated Scanner for Understanding MRI}
\acro{RF}{Radio Frequency}
\acro{RMSE}{Root Mean Squared Error}
\acro{RMSR}{Root Mean Squared Residual}
\acro{SA}{Simulated Annealing}
\acro{SNR}{Signal-to-Noise Ratio}
\acro{SPM}{Statistical Parametric Mapping}
\acro{T1}{Longitudinal}
\acro{T2}{Spin-Spin}
\acro{TR}{Repetition Time}
\acro{UKF}{Unscented Kalman Filter}
\end{acronym}
\pagebreak

\pagenumbering{arabic}
\pagestyle{myheadings}
\acresetall
\include{intro}
\include{background}
\include{particlefilters}
\include{methods}
\include{results}
\include{resultsB}
\include{discussion}
%\include{conclusion}

\clearpage
\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{plain}
%\bibliographystyle{abbrvnat}
%\bibliographystyle{apalike}
%\bibliographystyle{abbrvnat}
%\bibliographystyle{abbrv}
\bibliography{library}
